method

### 2022-02-03 06_Paper/ER-ED/method.Rmd
Update method.Rmd

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threi FlexER score.
Therefore, SVs will be ordered by magnitude.

>>>>

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threi FlexER score.
Therefore, SVs will be ordered by magnitude firstly. 
Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$. <!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? -->
